Submission to the Journal of the Royal Statistical Society, Series C (Applied Statistics) 

### 2024-02-19 manuscript_rss/appendix_2.Rmd
submission RSS

# options ----------------------------------------------------------------------
set.seed(123) # Seed for random number generation
options(scipen = 999) # disable sci number format
opts_chunk$set(
  cache.extra = rand_seed, 
  cache = FALSE,
  message = FALSE, 
  warning = FALSE, 
  error = FALSE,
  echo = FALSE, 
  fig.retina = 3,
  dev = "ragg_png"
  )

# variables --------------------------------------------------------------------
age_order <- c(
  "aged0to4", "aged5to9", "aged10to14", "aged15to19", "aged20to24",
  "aged25to34", "aged35to44", "aged45to54", "aged55to64", "aged65+"
)

# data -------------------------------------------------------------------------
te_results <- read_csv(here("data/te_results.csv")) |> 
    mutate(
      X = factor(X, levels = age_order),
      Y = factor(Y, levels = age_order)
    )
```

>>>>

# options ----------------------------------------------------------------------
set.seed(123) # Seed for random number generation
options(scipen = 999) # disable sci number format
opts_chunk$set(
  cache.extra = rand_seed, 
  cache = FALSE,
  message = FALSE, 
  warning = FALSE, 
  error = FALSE,
  echo = FALSE, 
  fig.retina = 3,
  dev = "ragg_png"
  )
```

```{r}
# variables --------------------------------------------------------------------
age_order <- c(
  "aged0to4", "aged5to9", "aged10to14", "aged15to19", "aged20to24",
  "aged25to34", "aged35to44", "aged45to54", "aged55to64", "aged65+"
)

# data -------------------------------------------------------------------------
te_results <- read_csv(here("data/te_results.csv")) |> 
    mutate(
      X = factor(X, levels = age_order),
      Y = factor(Y, levels = age_order)
    ) |> 
  select(-direction)
```

### 2024-02-19 manuscript_rss/cover_letter.Rmd
submission RSS

---
title: "Submission to Social Science & Medicine"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  error = FALSE, 
  echo = FALSE)
journal <- "Social Science & Medicine"
```

>>>>

---
title: "Submission to the Journal of the Royal Statistical Society, Series C (Applied Statistics) "
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  error = FALSE, 
  echo = FALSE)
journal <- "Journal of the Royal Statistical Society, Series C (Applied Statistics)"
```
